Rates of true polar wander in convecting planets

### 2014-05-13 tpw_rate.tex
Add some messy text

Convenient choices for these numbers are shown in Table \ref{nondim} along with approximate Earthlike values.
In addition to the more usual Rayleigh and Prandtl numbers we include a Froude number, characterizing the ratio of centrifugal to gravitational forces, and $\Gamma$, a nondimensional characterization of density variations.

@@

These equations are a version of what has been called the ``Milankovitch theorem'' \citep{munk1960rotation}.  
Written this way, it is clear that the important quantities are $\theta$, $\phi$, and the differences of the eigenvalues of the convective moment $\bf E$.
Thus it remains to derive estimates for these.

>>>>

Convenient choices for these numbers are shown in Table \ref{nondim} along with approximate Earthlike values.
In addition to the more usual Rayleigh and Prandtl numbers we include a Froude number, characterizing the ratio of centrifugal to gravitational forces, and $\Gamma$, a nondimensional characterization of density variations.
Nondimensionalizing with these parameters we obtain
\begin{equation}
\begin{aligned}
 - \nabla P^* + \; \nabla^2{\bf v} - \mathrm{Ra} \; T \; {\bf g} + \mathrm{Ra \; Fr}\; T \;{\bf \Omega \times \Omega \times r} = 0
\end{aligned}
\end{equation}

where we have introduced a dynamic pressure $P^* = P - P_0$.

@@

Without loss of generality we may choose the coordinate system such that $\phi=0$:
\begin{equation}
\dot{\theta} = - \frac{1}{2 \varepsilon \tau}\sin{2 \theta} \frac{(\lambda_3-\lambda_1)}{I_0}
\end{equation}

These equations are a version of what has been called the ``Milankovitch theorem'' \citep{munk1960rotation}.  
Written this way, it is clear that the important quantities are $\theta$ and the differences between the eigenvalues of the convective moment $\bf E$.
We may rewrite this in terms of the nondimensional numbers defined above, where $\varepsilon \sim \mathrm{Fr}$ and $\tau \sim \eta / \rho g R \sim \frac{R^2}{\kappa} \Gamma/\mathrm{Ra}$.

\begin{equation}
\dot{\theta} \sim - \frac{\mathrm{Ra}}{\Gamma \mathrm{Fr}} \sin{2 \theta} \frac{(\lambda_3-\lambda_1)}{I_0}
\end{equation}

Thus it remains to derive estimates for these.
